\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
added some new TODOs

\subsection{Simulating the "reddit effect"}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf 
against the HTTP content delivery latency under the throttled bandwidth conditions.

@@

\subsubsection{\zbf vs HTTP}
% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.

\begin{figure}[h]
% TODO: other plot here
% TODO: figure out ratio of seeders to leechers
\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of X seeders per leecher}
\end{figure}

>>>>

\subsection{Simulating the "reddit effect"}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 512 Kb/s (64 KB/s) and performed benchmark tests that compared the performance of \zbf
against the HTTP content delivery latency under the throttled bandwidth conditions.

@@

% TODO: Analyze the plot here

\subsubsection{\zbf vs HTTP}
Our next empirical analysis was to keep the ratio of seeders to leechers constant at 1:1, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.

\begin{figure}[h]
% TODO: other plot here
\caption{Average page load time over P2P compared to HTTP on throttled server assuming constant ratio of 1 seeder per leecher}
\end{figure}

% TODO: Analyze the plot here
